---
Title: Chapter 6 Exericses - FPP2
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---

```{r, echo = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = TRUE, fig.path = "Figures/Ch3/Ch3-")
library(forecast)
library(fpp2)
library(seasonal)
library(tidyverse)
devtools::install_github("thomasp85/patchwork")
library(patchwork)
```

## Forecasting: Principles and Practice - Chapter 6

### Exercise 2

The `plastics` data set consists of the monthly sales (in thousands) of product A for a plastics manufacturer for five years.

Plot the time series of sales of product A. Can you identify seasonal fluctuations and/or a trend-cycle?

   * Sales increase throughout the year, peaking in August and September and declining again in the 4th quarter of the year.

```{r, Exercise_2a, out.width ='33%', fig.show='hold'}
autoplot(plastics)
ggseasonplot(plastics)
ggsubseriesplot(plastics)
```
   
Use a classical multiplicative decomposition to calculate the trend-cycle and seasonal indices.

```{r, Exercise_2b, out.width ='50%'}
decompose(plastics, type = "multiplicative") %>% 
   autoplot() +
   ggtitle("Classical multiplicative decomposition")
```

Compute and plot the seasonally adjusted data.

```{r, Exercise_2c, out.width ='50%'}
autoplot(plastics) +
   autolayer(seasadj(decompose(plastics, type = "multiplicative")), series = "Seasonal Adj.") +
   xlab ("Year") + 
   ylab("Monthly Sales")
```

Change one observation to be an outlier (e.g., add 500 to one observation), and recompute the seasonally adjusted data. What is the effect of the outlier?

```{r, Exercise_2d, out.width ='50%'}
plastics_adj <- plastics
plastics_adj[17] <- plastics[17] + 500

autoplot(seasadj(decompose(plastics))) + 
   autolayer(seasadj(decompose(plastics_adj)), series = "Seasonal adj.\nwith Outlier")
```

Does it make any difference if the outlier is near the end rather than in the middle of the time series?

   * Yes, it makes a very big difference where the outlier is. If the outlier is at the end of the series, then prior values are not significantly impacted. The plot below shows that the seasonal adjustment with the outlier towards the end closely matches the seasonal adjustment of the original series untial the last few observations.

```{r, Exercise_2e,out.width ='50%'}
plastics_adj <- plastics
plastics_adj[58] <- plastics[58] + 500

autoplot(seasadj(decompose(plastics))) + 
   autolayer(seasadj(decompose(plastics_adj)), series = "Seasonal adj.\nwith Outlier")
```

### Exercise 3

Recall your retail time series data (from Exercise 3 in Section 2.10). Decompose the series using X11. Does it reveal any outliers, or unusual features that you had not noticed previously?

   * An X11 decomposition of the data reveal a strong change in the trend component and decline in seasonal component towards the end of the series.

```{r, Exercise_3a, out.width = '50%'}
retaildata <- readxl::read_excel("Data/retail.xlsx", skip = 1)
myts <- ts(retaildata[,"A3349873A"], frequency = 12, start = c(1982, 4))
autoplot(myts)
x11_adj <- seas(myts, x11 = "")
autoplot(x11_adj)
```

### Exercise 4

Figures [6.16](https://otexts.com/fpp2/fpp_files/figure-html/labour-1.png) and [6.17](https://otexts.com/fpp2/fpp_files/figure-html/labour2-1.png) show the result of decomposing the number of persons in the civilian labour force in Australia each month from February 1978 to August 1995.


Write about 3–5 sentences describing the results of the decomposition. Pay particular attention to the scales of the graphs in making your interpretation.

   * The series decomposition exhibit a strong upwards trend, which accounts for the majority of the variation in the series. A very small seasonal component reflects staff fluctiations ranging between +50 and -50. The residual component of the series is relatively small (below 100) for most of the series except for a period just after 1990 which shows significant negative residuals of over -300 to -400. 

Is the recession of 1991/1992 visible in the estimated components?

   * Yes, the recession is clearly visible in the residual component of the decomposition, which has far stronger negative values than any other periods. 

### Exercise 5

This exercise uses the `cangas` data (monthly Canadian gas production in billions of cubic metres, January 1960 – February 2005).

Plot the data using `autoplot()`, `ggsubseriesplot()` and `ggseasonplot()` to look at the effect of the changing seasonality over time. What do you think is causing it to change so much?

   * The changes in seasonality could have many causes. One possibility, is that larger than usual temperature swings (very warm summers and very cold winters) led to greater variation in the demand for gas.

```{r, Exercise_5a, out.width = '33.%', fig.show = 'hold'}
autoplot(cangas)
ggsubseriesplot(cangas)
ggseasonplot(cangas)
```

Do an STL decomposition of the data. You will need to choose `s.window` to allow for the changing shape of the seasonal component.

```{r, Exercise_5b, fig.width = 20, fig.height = 10}
cangas_stl <- stl(cangas, s.window = 10)
cangas_x11 <- seas(cangas, x11 = "") 
cangas_seats <- seas(cangas)

stl <- autoplot(cangas) +
   autolayer(seasadj(cangas_stl), series = "Seasonal Adj.") +
   autolayer(trendcycle(cangas_stl), series = "Trend") + 
   ggtitle("Cangas: STL Decomposition")

x11 <- autoplot(cangas) +
   autolayer(seasadj(cangas_x11), series = "Seasonal Adj.") +
   autolayer(trendcycle(cangas_x11), series = "Trend") + 
   ggtitle("Cangas: X11 Decomposition")

seats <- autoplot(cangas) +
   autolayer(seasadj(cangas_seats), series = "Seasonal Adj.") +
   autolayer(trendcycle(cangas_seats), series = "Trend") + 
   ggtitle("Cangas: SEATS Decomposition")

stl + x11 + seats
```

### Exercise 6

We will use the `bricksq` data (Australian quarterly clay brick production. 1956–1994) for this exercise.

Use an STL decomposition to calculate the trend-cycle and seasonal indices. (Experiment with having fixed or changing seasonality.)

```{r, Exercise_6a}
autoplot(bricksq) +
   ggtitle("Quarterly clay brick production")

constant <- autoplot(stl(bricksq, s.window = "periodic", robust = TRUE)) + 
   ggtitle("Quarterly clay brick production: \nSTL decomposition with fixed seasonality")

changing <- autoplot(stl(bricksq, s.window = 10, robust = TRUE)) + 
   ggtitle("Quarterly clay brick production: \nSTL decomposition with changing seasonality")

constant + changing
```

Compute and plot the seasonally adjusted data.

```{r, Exercise_6b}
bricksq_adj <- seasadj(stl(bricksq, s.window = 10, robust = TRUE))

autoplot(bricksq_adj) + 
   ggtitle("Quarterly clay brick production: Seasonal Adjusted")
```

Use a naïve method to produce forecasts of the seasonally adjusted data.

```{r, Exercise_6c}
bricksq_fct <- naive(bricksq_adj, h = 8)

autoplot(bricksq_fct)
```

Use `stlf()` to reseasonalise the results, giving forecasts for the original data.

```{r, Exercise_6d}
stl_fct <- stlf(bricksq, h = 8, method = "naive")

autoplot(stl_fct)
```

Do the residuals look uncorrelated?

   * The residuals do not appear uncorrelated. A Ljung-Box test for autocorrelation rejects the null hypothesis of no autocorrelation in the residuals at the 1% significance level. Additionally, an ACF plot shows significant autocorrelation at lags 1, 5 and 8. 

```{r, Exercise_6e}
checkresiduals(stl_fct)
```

Repeat with a robust STL decomposition. Does it make much difference?

   * Using a robust does not make a significant difference in reducing residual autocorrelation. 

```{r, Exercise_6f}
stl_fct_robust <- stlf(bricksq, h = 8, method = "naive", robust = TRUE)

checkresiduals(stl_fct_robust)
```

Compare forecasts from stlf() with those from snaive(), using a test set comprising the last 2 years of data. Which is better?

   * According to the RMSE and MASE, the STL forecasting method provides both better in sample and out of sample predictions. 

```{r, Exercise_6g, eval = FALSE}
train <- window(bricksq, start = 1956, end = c(1992, 3))
test <- window(bricksq, start = c(1992, 4))

slf_fct <- stlf(train, h = 8, method = "naive")
snaive_fct <- snaive(train, h = 8)

autoplot(train) + 
   autolayer(slf_fct, PI = FALSE, alpha = 0.5) + 
   autolayer(snaive_fct, PI = FALSE, color = "red", alpha = 0.5)

# accuracy of STL forecast
accuracy(slf_fct, test)
#accuracy of seasonal naive forecast
accuracy(snaive_fct, test)
```

```{r, Exercise_6h, echo = FALSE}
train <- window(bricksq, start = 1956, end = c(1992, 3))
test <- window(bricksq, start = c(1992, 4))

slf_fct <- stlf(train, h = 8, method = "naive")
snaive_fct <- snaive(train, h = 8)

autoplot(train) + 
   autolayer(slf_fct, PI = FALSE, alpha = 0.5) + 
   autolayer(snaive_fct, PI = FALSE, color = "red", alpha = 0.5)

# accuracy of STL forecast
accuracy(slf_fct, test)
#accuracy of seasonal naive forecast
accuracy(snaive_fct, test)
```

### Exercise 7 

Use `stlf()` to produce forecasts of the `writing` series with either `method = "naive"` or `method = "rwdrift"`, whichever is most appropriate. Use the lambda argument if you think a Box-Cox transformation is required.

   * A random walk with drift forecast using STL decomposition provides better in-sample fit than the naive method.

```{r, Exercise_7a}
autoplot(writing) + 
   ggtitle("Sales of printing and writing paper") + 
   ylab("Thousands of French Francs")
```

```{r, Exercise_7b}
naive_fct <- stlf(writing, h = 12, method = "naive")
rwdrift_fct <- stlf(writing, h = 12, method = "rwdrift")

autoplot(naive_fct)

autoplot(rwdrift_fct)

accuracy(naive_fct)
accuracy(rwdrift_fct)
```


### Exercise 8

Use `stlf()` to produce forecasts of the `fancy` series with either `method = "naive"` or `method = "rwdrift"`, whichever is most appropriate. Use the lambda argument if you think a Box-Cox transformation is required.

```{r, Exercise_8a}
autoplot(fancy) +
   ggtitle("Sales for a souvenir shop")
```

```{r, Exercise_8b}
fancy_fct <- stlf(fancy, h = 12, method = "rwdrift", lambda = BoxCox.lambda(fancy))

autoplot(fancy_fct)
```











